Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-06 paper.tex
Composition (not finished)

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to some learning algorithm, some estimators in the library implement
a \textit{transformer} interface which defines a \texttt{transform} method
taking as input some dataset \texttt{X} and yielding as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

@@

A distinguishing feature of scikit-learn estimators
is that they can be composed into \texttt{Pipeline} objects.
Such objects combine typical machine learning workflows
(extracting features, centering/scaling/normalization,
feature selection, making predictions)
in a single object that is itself an estimator,
and whose methods cause data to flow through the pipeline.
More importantly, though, they can be used for
systematic, automated model selection.
This is best explained by example.

>>>>

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement
a \textit{transformer} interface which defines a \texttt{transform} method
taking as input some dataset \texttt{X} and yielding as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

@@

A distinguishing feature of the \textit{scikit-learn} API is its ability to
compose new estimators from other estimators. Such objects combine typical
machine learning  workflows (e.g., feature extraction,
centering/scaling/normalization, feature selection, learning) into  a single
object which is itself an estimator. As such, composed estimators can be used
anywhere usual estimators are used. In particular, they can be used within model
selection routines, allowing one to optimize at once every step of a complex
workflow. Composition of estimators can be done in two ways: either sequentially
through \texttt{Pipeline} objects or in a parallel fashion through
\texttt{FeatureUnion} objects.

\vspace{3cm}

A distinguishing feature of \textit{scikit-learn} estimators
is that they can be composed into \texttt{Pipeline} objects.
Such objects combine typical machine learning workflows
(extracting features, centering/scaling/normalization,
feature selection, making predictions)
in a single object that is itself an estimator,
and whose methods cause data to flow through the pipeline.
More importantly, though, they can be used for
systematic, automated model selection.
This is best explained by example.
